\documentclass[12pt,a4paper]{article}

% ========== Packages ==========
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{thmtools}
\usepackage{xcolor}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{fancyhdr}

\geometry{margin=1in, headheight=14.5pt}
\onehalfspacing

% ========== Theorem Environments ==========
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{remark}[theorem]{Remark}

% ========== Custom Commands ==========
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\KL}{D_{\mathrm{KL}}}
\newcommand{\TV}[2]{\left\|#1 - #2\right\|}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\conv}{\operatorname{conv}}
\DeclareMathOperator*{\argmax}{argmax}
\newcommand{\OT}{\mathrm{OT}}
\DeclareMathOperator*{\liminff}{\underline{\lim}}
\DeclareMathOperator*{\limsupf}{\overline{\lim}}

% ========== Auto-generated Statistics ==========
\input{stats}

% ========== Header/Footer ==========
\pagestyle{fancy}
\fancyhf{}
\rhead{\small Extending Marginal Reputation to Markov States}
\lhead{\small \thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ========== Colors for hyperref ==========
\hypersetup{
    colorlinks=true,
    linkcolor=blue!70!black,
    citecolor=green!50!black,
    urlcolor=blue!60!black
}

% ================================================================
\begin{document}

% ========== Title Page ==========
\begin{titlepage}
\centering
\vspace*{2cm}

{\LARGE\bfseries Extending Marginal Reputation\\[6pt]
to Persistent Markovian States}

\vspace{1.5cm}

{\large
Kyle Elliott Mathewson\textsuperscript{1} \\[6pt]
with AI Collaborators
}

\vspace{1.5cm}

{\large \PaperDate}

\vspace{1cm}

\noindent\textsuperscript{1}Faculty of Science, University of Alberta

\vspace{2cm}

\begin{abstract}
\noindent
We extend the main result (Theorem~1) of Luo \& Wolitzky (2024), ``Marginal Reputation,'' from i.i.d.\ states to persistent Markovian states. The extension reveals a new phenomenon: when the Stackelberg strategy reveals the state, short-run player beliefs permanently deviate from the stationary distribution, causing the Nash correspondence to become state-contingent. We introduce the concept of \emph{belief-robustness} and present two results. \textbf{Theorem~1\textsuperscript{$\prime$}} (belief-robust case): when short-run best responses are invariant to the filtering belief $F(\cdot|\theta)$, the original commitment payoff $V(s_1^*)$ holds exactly under Markov states with no correction. \textbf{Theorem~1\textsuperscript{$\prime\prime$}} (general case): the \emph{Markov commitment payoff} $V_{\mathrm{Markov}}(s_1^*) = \sum_\theta \pi(\theta) \cdot \inf_{B(s_1^*, F(\cdot|\theta))} u_1 \leq V(s_1^*)$ provides the appropriate bound, with equality if and only if the game is belief-robust. The gap $V(s_1^*) - V_{\mathrm{Markov}}$ quantifies the \emph{cost of persistence in reputation games}---a new economic object measuring how state persistence enables short-run players to condition behavior on the revealed state. For the deterrence game with baseline parameters ($\alpha=\BaseAlpha$, $\beta=\BaseBeta$), this cost is \PayoffOverestimation\% of the i.i.d.\ payoff. Our framework interpolates continuously between i.i.d.\ (Luo--Wolitzky) and perfectly persistent (Pei 2020) states. The paper also documents the human--AI research process, including computational verification across seven analysis modules with eight diagnostic figures.
\end{abstract}

\vspace{0.5cm}

\noindent\textbf{Keywords:} Reputation, repeated games, Markov states, optimal transport, belief-robustness, corrected bounds

\vspace{0.5cm}

\noindent\textbf{Original Paper:} ``Marginal Reputation'' by Daniel Luo and Alexander Wolitzky, MIT Department of Economics, December 2024.

\end{titlepage}

% ========== Table of Contents ==========
\tableofcontents
\newpage

% ========== Main Sections ==========
\input{sections/sec_01_intro}
\input{sections/sec_02_model}
\input{sections/sec_03_belief_robustness}
\input{sections/sec_04_theorems}
\input{sections/sec_05_proof}
\input{sections/sec_06_supermodular}
\input{sections/sec_07_example}
\input{sections/sec_08_interpolation}
\input{sections/sec_09_methodology}
\input{sections/sec_10_discussion}

% ========== Appendices ==========
\appendix
\input{sections/app_A_kl_verification}
\input{sections/app_B_computational}

% ========== References ==========
\section*{References}
\addcontentsline{toc}{section}{References}

\begin{enumerate}[label={[\arabic*]}, leftmargin=*, itemsep=3pt]
\item Chigansky, P.\ and R.\ Liptser (2004). ``Stability of nonlinear filters in nonmixing case.'' \textit{Annals of Applied Probability}, 14(4): 2038--2056.

\item Cover, T.\ M.\ and J.\ A.\ Thomas (2006). \textit{Elements of Information Theory}, 2nd ed. Wiley.

\item Del Moral, P.\ (2004). \textit{Feynman--Kac Formulae: Genealogical and Interacting Particle Systems with Applications}. Springer.

\item Fudenberg, D.\ and D.\ K.\ Levine (1992). ``Maintaining a Reputation When Strategies Are Imperfectly Observed.'' \textit{Review of Economic Studies}, 59(3): 561--579.

\item Gossner, O.\ (2011). ``Simple Bounds on the Value of a Reputation.'' \textit{Econometrica}, 79(5): 1627--1651.

\item Luo, D.\ and A.\ Wolitzky (2024). ``Marginal Reputation.'' MIT Department of Economics Working Paper.

\item Mailath, G.\ J.\ and L.\ Samuelson (2006). \textit{Repeated Games and Reputations: Long-Run Relationships}. Oxford University Press.

\item Pei, H.\ (2020). ``Reputation Effects under Interdependent Values.'' \textit{Econometrica}, 88(5): 2175--2202.

\item Rochet, J.-C.\ (1987). ``A Necessary and Sufficient Condition for Rationalizability in a Quasi-linear Context.'' \textit{Journal of Mathematical Economics}, 16(2): 191--200.

\item Santambrogio, F.\ (2015). ``Optimal Transport for Applied Mathematicians.'' Birkh\"auser.
\end{enumerate}

\end{document}
